---
title: "Week02Prj01RM1"
author: "Chirag S"
date: "8/31/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(haven)
library(psych)
library(here)


```

Reading Data
Naming data > can use of Camel (xAcC) vs Snake case (x_A_cC)
We have a Stata file so we use the 'haven' package to read it.

```{r}

Week02Prj1RM1F1D1 <- haven::read_dta("tech_co_cstat_dta.zip") # :: reads a stata file comes from haven package

```

Understanding the Class

```{r}
class(Week02Prj1RM1F1D1)

```
Understanding Data Frame

```{r}

names(Week02Prj1RM1F1D1)

```
Understanding Data Set
head shows the first 6 rows

```{r}
head(Week02Prj1RM1F1D1, n = 10)

```

Tail shows the last 6 rows of the data set

```{r}
tail(Week02Prj1RM1F1D1, n = 15)
```


Head function with specific data

```{r}
Week02Prj1RM1F1D1[50:65]
```


how to look at metadata of a variable
for a specific attribute, select $ sign. 

```{r}
attributes(Week02Prj1RM1F1D1$datadate)

```

how to rewrite an attribute label with more descriptive

```{r}
attributes(Week02Prj1RM1F1D1$datadate)$label <- "Fiscal Year End Date"

```

Now check the modified name of the attribute

```{r}
attributes(Week02Prj1RM1F1D1$datadate)
```

how to remove attribute

```{r}
attributes(Week02Prj1RM1F1D1$datadate)$label <- NULL
```

NOW CHECK THE REMOVED VALUE. 

```{r}
attributes(Week02Prj1RM1F1D1$datadate)
```

