---
title: "Week02Prj01RM1"
author: "Chirag S"
date: "8/31/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(haven)
library(psych)
library(here)


```

Reading Data
Naming data > can use of Camel (xAcC) vs Snake case (x_A_cC)
We have a Stata file so we use the 'haven' package to read it.

```{r}

Week02Prj1RM1F1D1 <- haven::read_dta("tech_co_cstat_dta.zip") # :: reads a stata file comes from haven package

```

Understanding the Class

```{r}
class(Week02Prj1RM1F1D1)

```
Understanding Data Frame

```{r}

names(Week02Prj1RM1F1D1)

```
Understanding Data Set
head shows the first 6 rows

```{r}
head(Week02Prj1RM1F1D1, n = 10)

```

Tail shows the last 6 rows of the data set

```{r}
tail(Week02Prj1RM1F1D1, n = 15)
```


Head function with specific data

```{r}
Week02Prj1RM1F1D1[50:65]
```


how to look at metadata of a variable
for a specific attribute, select $ sign. 

```{r}
attributes(Week02Prj1RM1F1D1$datadate)

```

how to rewrite an attribute label with more descriptive

```{r}
attributes(Week02Prj1RM1F1D1$datadate)$label <- "Fiscal Year End Date"

```

Now check the modified name of the attribute

```{r}
attributes(Week02Prj1RM1F1D1$datadate)
```

how to remove attribute

```{r}
attributes(Week02Prj1RM1F1D1$datadate)$label <- NULL
```

NOW CHECK THE REMOVED VALUE. 

```{r}
attributes(Week02Prj1RM1F1D1$datadate)
```

----------------------------
09/07/2021 Class Exercises
----------------------------

```{r}
glimpse(Week02Prj1RM1F1D1)

```


```{r}

psych::describe(Week02Prj1RM1F1D1)

```

```{r}

table(Week02Prj1RM1F1D1$gvkey)

```

```{r}
count(Week02Prj1RM1F1D1, conm)
```
##Select()

```{r}

d2 <- select(Week02Prj1RM1F1D1, conm, datadate, sale, xrd)

```

```{r}

names(d2)

```

```{r}
d2 <- select (Week02Prj1RM1F1D1, -gvkey)
```

```{r}

d3 <- Week02Prj1RM1F1D1 %>% 
  select (-gvkey) %>% 
  head()

```


```{r}

d4 <- head(select(Week02Prj1RM1F1D1, -gvkey))

```

```{r}

identical(d3, d4)
```

```{r}
mean(Week02Prj1RM1F1D1$sale, na.rm = TRUE)


```
```{r}

head(Week02Prj1RM1F1D1$sale, 10)

```
```{r}

d5 <- Week02Prj1RM1F1D1 %>% 
         filter(sale > 0)
```



```{r}

mean(d5$sale)

```


```{r}

d5 <- Week02Prj1RM1F1D1 %>% 
  filter(is.na(sale))
```


```{r}

!is.na(Week02Prj1RM1F1D1$sale)

```
TO TURN OFF THE CODE AND OUTPUT 


### Mutate()

```{r}

d7 <- d5 %>% 
  mutate(profit_margin = oibdp / sale)
```


```{r}

names(d7)
```

```{r}

d7 <- d5 %>% 
  mutate(profit_margin = oibdp / sale, 
          cash_holding = che / at,
          rnd_intensity = xrd / sale,
          debt_lt = ifelse(is.na(dltt),0, dltt))

```



```{r}
head(d5$dltt) 

```


```{r}

is.na(d5$dltt) %>%  sum()

```



```{r}
is.integer(d7$cash_holding)

class(d7$cash_holding)

```
```{r}


d7 %>% 
  select (conm, datadate, sale) %>% 
  head(20)
  
```

```{r}

d8 <- d7 %>% 
  arrange (conm, datadate) %>% 
  group_by(conm) %>% 
  mutate(sales_gr = (sale - lag(sale))/ lag(sale)) #provides sales growth

```


```{r}

d8 %>% 
  select (conm, datadate, sale, sales_gr) %>% 
  head(20)
```

```{r}


d7 %>% 
  select(sale) %>% 
  summarize(sale_mean = mean(sale),
            sales_median = median(sale),
            sale_sd = sd(sale))
```
```{r}

d7 %>% 
  select(sale, at, xrd) %>% 
  summarize(across(everything(), mean))

```

```{r}

d7 %>% 
  group_by(conm) %>% 
  summarize(sale_mean = mean(sale),
            sales_median = median(sale),
            sale_sd = sd(sale)) %>% 
 as.data.frame ()
```


```{r}

d5 %>% 
  mutate(first_half_decade = ifelse(fyear <2015, 1, 0)) %>% 
  group_by (conm, first_half_decade) %>% 
   summarize(sale_mean = mean(sale),
            sales_median = median(sale),
            sale_sd = sd(sale)) %>% 
  as.data.frame ()
  
```

